|

### 2023-04-27 manuscript/Chapter2-appendix1.Rmd
update appendices 1 and 3

```{r figS4, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice. The difference is displayed on the x axis and the parameter correlations are displayed on the y axis."}

>>>>

```{r figS4, out.width = "80%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice. The difference is displayed on the x axis and the parameter correlations are displayed on the y axis."}

### 2023-04-27 manuscript/Chapter2-appendix3.Rmd
update appendices 1 and 3

```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice. The difference is displayed on the x axis and the parameter correlations are displayed on the y axis. The results are from the MDHGLM that includes the outlier."}

>>>>

```{r figS2, out.width = "80%", fig.cap = "**Figure S2.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice. The difference is displayed on the x axis and the parameter correlations are displayed on the y axis. The results are from the MDHGLM that includes the outlier."}
